---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  geno: "no data"
  rep: "no data"
  block: "no data"
  k: "no data"
  dfr: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo = FALSE}
library(knitr)

traits <- params$traits
geno <- params$geno
rep <- params$rep
block <- params$block
k <- params$k
dfr <- params$dfr

out <- rm.fna(c('geno', 'block', 'rep'), dfr)
dfr <- out$dfr
nmis.fac <- out$nmis.fac

lc <- ck.fs(c('geno', 'block'), 'rep', dfr)
ng <- lc$nl[[1]]
nrep <- lc$nrep
nib <- lc$nl[[2]]

block <- dfr[, block]
geno <- dfr[, geno]
rep <- dfr[, rep]
```

# 1. Model specification and data description

There are data for `r ng` genotypes tested using an alpha (0,1) design with `r nrep` replications and `r nib` incomplete blocks. In this design each replication is a complete block for the genotypes that is splitted in several incomplete blocks. The statistical model is
$$
y_{ijk} = \mu + \tau_i + \gamma_j + \rho_{k(j)} + \epsilon_{ijk}
$$
where

* $y_{ijk}$ is the observed response with genotype $i$, replication $j$, incomplete block $k$.
* $\mu$ is the mean response over all genotypes and replications.
* $\tau_i$ is the effect for genotype $i$.
* $\gamma_j$ is the effect for replication $j$.
* $\rho_{k(j)}$ is the effect of the incomplete block $k$ which is nested into replication $j$.
* $\epsilon_{ijk}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ijk} \sim N(0,\sigma_{\epsilon}^2)$.

```{r include = FALSE}
out <- NULL
for (i in 1:length(traits))
  out <- c(out, knit_expand('child_a01d.Rmd'))
```

`r paste(knit(text = out), collapse = '\n')`
