`r i = {{i}}`

```{r, echo = FALSE}
lc <- ck.f(traits[i], factors, rep, data)
if (lc$c4 == 0) {
  trait.est <- paste(traits[i], ".est", sep = "")
  data$est <- mve.f(traits[i], factors, rep, design, data, maxp)[, trait.est]
  } else {
    data$est <- data[, traits[i]]
  }
```
    
# {{i+1}}. Analysis for trait `r traits[i]`

`r if (lc$c4 == 1) {"There are no missing values for this trait; the design is balanced."}`

`r if (lc$c4 == 0) paste("There are some missing values (", format(lc$pmis * 100, digits = 3), "%) and they have been estimated for the descriptive statistics and ANOVA.", sep = "")`

## {{i+1}}.1. Descriptive statistics

### {{i+1}}.1.1. Means by individual factor levels

```{r, echo = FALSE}
for (j in 1:lc$nf)
  tapply(data$est, data[, factors[j]], mean)
```

### {{i+1}}.1.2. Means by factor levels combinations

```{r, echo = FALSE}
# Create expression for list of factors
  
lf.expr <- 'list(data[, factors[1]]'
  
for (j in 2:nf)
  lf.expr <- paste(lf.expr, ', data[, factors[', j, ']]', sep = "")
  
lf.expr <- paste(lf.expr, ')', sep = "")

# Compute means over replications

tapply(data$est, eval(parse(text = lf.expr)), mean)
```

## {{i+1}}.2. ANOVA

### {{i+1}}.2.1. Checking assumptions

As it was stated in section 1, it is supposed that the error has a normal distribution with the same variance for all the combinations among the levels of the factors. The following plots help to evaluate this assumptions:

```{r, echo = FALSE, fig.height = 5, fig.width = 10}
# ANOVA
  
expr <- paste(traits[i], '~', factors[1])
for (j in 2:lc$nf)
  expr <- paste(expr, '*', factors[j])

if (design == "crd") {
  ff <- as.formula(expr)
  model <- aov(ff, data = data)
}
  
if (design == "rcbd") {
  expr <- paste(expr, '+', rep)
  ff <- as.formula(expr)
  model <- aov(ff, data = data)
}

par(mfrow = c(1, 2))
suppressWarnings(plot(model, which = 1))
suppressWarnings(plot(model, which = 2))
```

Funnel shapes for the first plot may suggest heterogeneity of variances while departures from the theoretical normal line are symptoms of lack of normality.

### {{i+1}}.2.2. ANOVA table

```{r, echo = FALSE}
at <- suppressWarnings(aov.f(traits[i], factors, rep, design, data, maxp))
at
```
