`r i = {{i}}`

# {{i+1}}. Analysis for trait `r traits[i]`

```{r, echo = FALSE}
lc <- check.rcbd(traits[i], geno, rep, data)
```

`r if (lc$c2 == 0) {"There is only one replication. Analysis is not possible with one replication."}`

`r if (lc$c2 == 1 & lc$c3 == 0) {"There is more than one datum for some genotype/replication combination. This could be the result of a mislabeling for the levels of the factors. The table below shows the frequencies of valid data for each genotype in each replication. Check this to proceed."}`

`r if (lc$c1 == 0 & lc$c2 == 1 & lc$c3 == 1) {"The table below shows the frequencies of valid data for each genotype in each replication. There are some genotypes without data. Remove these genotypes to proceed."}`

`r if (lc$pmis > maxp & lc$c1 == 1 & lc$c2 == 1 & lc$c3 == 1) paste("There are too many missing values (", format(lc$pmis * 100, digits = 3), "%). The table below shows the frequencies of valid data for each genotype in each replication. This procedure estimates up to 10%. Remove some genotypes to proceed.", sep = "")`

```{r, echo = FALSE}
if (lc$c2 == 1)
  lc$tfreq
```
