`r i = {{i}}`

# {{i+1}}. Analysis for trait `r traits[i]`

```{r, echo = FALSE}
nt <- nlevels(as.factor(data[, treat]))
model <- aov(data[, traits[i]] ~ data[, treat])
at <- anova(model)
```

## {{i+1}}.1. ANOVA

You have fitted a linear model for a CRD. The ANOVA table for your model is:

```{r, echo = FALSE}
at
```

The p-value for treatments is `r format(at[1, 5], digits = 4)`
`r if(at[1, 5] < 0.05) {"which is significant at the 5% level."} else {"which is not significant at the 5% level."}`

## {{i+1}}.2. Assumptions

Don't forget the assumptions of the model. It is supposed that the error has a normal distribution with the same variance for all the treatments. The following plots must help you evaluate this:

```{r, echo = FALSE, fig.height = 5, fig.width = 10}
par(mfrow = c(1, 2))
plot(model, which = 1)
plot(model, which = 2)
```

Funnel shapes for the first plot may suggest heterogeneity of variances while departures from the theoretical normal line are symptoms of lack of normality.

## {{i+1}}.3. Treatment means

`r if(at[1, 5] < 0.05) {"Below are the sorted means for each treatment with letters indicating if there are significant differences using the multiple comparisons method of Tukey at the 5% level."} else {"The means of your treatments are:"}`

```{r, echo = FALSE}
if (at[1, 5] < 0.05)
  agricolae::HSD.test(data[, traits[i]], data[, treat], at[2, 1], at[2, 3])$groups else
    tapply(data[, traits[i]], data[, treat], mean, na.rm = TRUE)
```

`r if(nt < 10) {"It is always good to have some visualization of the data. Because the number of treatments in your experiment is not so big, we can plot the data for each treatment:"}`

```{r, echo = FALSE}
if (nt < 10) msdplot(traits[i], treat, data, conf = 1)
```

## {{i+1}}.4. Variance components

Below are the variance components for this model, under the assumption that treatments are random. Here the model is fitted using REML.

```{r, echo = FALSE}
ff <- as.formula(paste(traits[i], "~ (1|", treat, ")"))
fm <- lme4::lmer(ff, data = data)
lme4::VarCorr(fm)
```

