`r i = {{i}}`

# {{i+1}}. Analysis for trait `r traits[i]`

```{r, echo = FALSE}
lc <- check.2f(traits[i], geno, env, rep, data)
```

`r if (lc$c2 == 0) {"There is only one replication. Analysis is not possible with one replication."}`

`r if (lc$c2 == 1 & lc$c3 == 0) {"There is more than one datum for some environment/genotype/replication combination. This could be the result of a mislabeling for the levels of the factors. The table below shows the frequencies of valid data for each genotype in each environment. Check this to proceed."}`

`r if (lc$c1 == 0 & lc$c2 == 1 & lc$c3 == 1) {"The table below shows the frequencies of valid data for each genotype in each environment. There are some genotypes with zero frequency in some environments. A MET analysis cannot be produce with zero frequencies so you should remove genotypes or environments to proceed."}`

`r if (lc$pmis > maxp & lc$c1 == 1 & lc$c2 == 1 & lc$c3 == 1) paste("There are too many missing values (", format(lc$pmis * 100, digits = 3), "%). The table below shows the frequencies of valid data for each genotype in each environment. This procedure estimates up to 10%. Remove some genotypes or environments to proceed.", sep = "")`

```{r, echo = FALSE}
if (lc$c2 == 1 & lc$c3 == 1)
  lc$tfreq
if (lc$c2 == 1 & lc$c3 == 0)
  lc$tfreqr
```
