`r i = {{i}}`

# {{i+1}}. Analysis for trait `r traits[i]`

```{r results = 'hide'}
y <- dfr[, traits[i]]

if (is.null(sspf)) {
  model <- agricolae::sp.plot(dfr[, rep], dfr[, mpf], dfr[, spf], y)
} else {
  model <- agricolae::ssp.plot(dfr[, rep], dfr[, mpf], dfr[, spf], dfr[, sspf], y)
}
```

## {{i+1}}.1. ANOVA

```{r}
at <- model$ANOVA
if (is.null(sspf)) {
  rownames(at) <- c(rep, mpf, 'Ea', spf, paste(mpf, spf, sep = ':'), 'Eb')
} else {
  rownames(at) <- c(rep, mpf, 'Ea', spf, paste(mpf, spf, sep = ':'), 'Eb',
                    sspf, paste(mpf, sspf, sep = ':'), paste(spf, sspf, sep = ':'),
                    paste(mpf, spf, sspf, sep = ':'), 'Ec')
}
at
```

## {{i+1}}.2. Tukey test for full treatments

Note: This test is produced regardless of the significance of any term in the ANOVA model. The main purpose here is to show a sorted table of means as reference.

```{r}
if (is.null(sspf)) {
  dfr$t.full <- paste(dfr[, mpf], dfr[, spf], sep = '_')
  agricolae::HSD.test(y, dfr$t.full, at[6, 1], at[6, 3])$groups
} else {
  dfr$t.full <- paste(dfr[, mpf], dfr[, spf], dfr[, sspf], sep = '_')
  agricolae::HSD.test(y, dfr$t.full, at[11, 1], at[11, 3])$groups
}
```

`r if (is.null(sspf) & (at[2, 5] < 0.05 | at[5, 5] < 0.05)) {paste0("## ", {{i+1}}, ".3. LSD test for ", mpf)}`

```{r}
if (is.null(sspf) & at[2, 5] < 0.05 & (at[5, 5] > 0.05 | pe)) {
  y <- dfr[, traits[i]]
  agricolae::LSD.test(y, dfr[, mpf], at[3, 1], at[3, 3])$groups
}

if (is.null(sspf) & at[5, 5] < 0.05) {
  for (j in 1:nspf) {
    temp <- dfr[dfr[, spf] == unique(dfr[, spf])[j], ]
    y <- temp[, traits[i]]
    print(paste("LSD test for", spf, unique(dfr[, spf])[j]))
    print(agricolae::LSD.test(y, temp[, mpf], at[6, 1], at[6, 3])$groups)
    cat("\n")
  }
}
```

`r if (is.null(sspf) & (at[2, 5] < 0.05 | at[5, 5] < 0.05)) {paste0("## ", {{i+1}}, ".4. Tukey test for ", mpf)}`

```{r}
if (is.null(sspf) & at[2, 5] < 0.05 & (at[5, 5] > 0.05 | pe)) {
  y <- dfr[, traits[i]]
  agricolae::HSD.test(y, dfr[, mpf], at[3, 1], at[3, 3])$groups
}

if (is.null(sspf) & at[5, 5] < 0.05) {
  for (j in 1:nspf) {
    temp <- dfr[dfr[, spf] == unique(dfr[, spf])[j], ]
    y <- temp[, traits[i]]
    print(paste("HSD Tukey test for", spf, unique(dfr[, spf])[j]))
    print(agricolae::HSD.test(y, temp[, mpf], at[6, 1], at[6, 3])$groups)
    cat("\n")
  }
}
```

`r if (is.null(sspf) & (at[4, 5] < 0.05 & at[2, 5] > 0.05 & at[5, 5] > 0.05)) {paste0("## ", {{i+1}}, ".3. LSD test for ", spf)}`
`r if (is.null(sspf) & (at[5, 5] < 0.05 | (at[2, 5] < 0.05 & at[4, 5] < 0.05))) {paste0("## ", {{i+1}}, ".5. LSD test for ", spf)}`

```{r}
if (is.null(sspf) & at[4, 5] < 0.05 & (at[5, 5] > 0.05 | pe)) {
  y <- dfr[, traits[i]]
  agricolae::LSD.test(y, dfr[, spf], at[6, 1], at[6, 3])$groups
}

if (is.null(sspf) & at[5, 5] < 0.05) {
  for (j in 1:nmpf) {
    temp <- dfr[dfr[, mpf] == unique(dfr[, mpf])[j], ]
    y <- temp[, traits[i]]
    print(paste("LSD test for ", mpf, unique(dfr[, mpf])[j]))
    print(agricolae::LSD.test(y, temp[, spf], at[6, 1], at[6, 3])$groups)
    cat("\n")
  }
}
```

`r if (is.null(sspf) & (at[4, 5] < 0.05 & at[2, 5] > 0.05 & at[5, 5] > 0.05)) {paste0("## ", {{i+1}}, ".4. Tukey test for ", spf)}`
`r if (is.null(sspf) & (at[5, 5] < 0.05 | (at[2, 5] < 0.05 & at[4, 5] < 0.05))) {paste0("## ", {{i+1}}, ".6. Tukey test for ", spf)}`

```{r}
if (is.null(sspf) & at[4, 5] < 0.05 & (at[5, 5] > 0.05 | pe)) {
  y <- dfr[, traits[i]]
  agricolae::HSD.test(y, dfr[, spf], at[6, 1], at[6, 3])$groups
}

if (is.null(sspf) & at[5, 5] < 0.05) {
  for (j in 1:nmpf) {
    temp <- dfr[dfr[, mpf] == unique(dfr[, mpf])[j], ]
    y <- temp[, traits[i]]
    print(paste("HSD Tukey test for ", mpf, unique(dfr[, mpf])[j]))
    print(agricolae::HSD.test(y, temp[, spf], at[6, 1], at[6, 3])$groups)
    cat("\n")
  }
}
```
