---
title: "Authomatic report for a Completely Randomized Design (CRD)"
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  treat: "no data"
  data: "no data"
  maxp: "no data"
  author: "no data"
---

```{r, echo = FALSE}
library(knitr)

traits <- params$traits
treat <- params$treat
data <- params$data
maxp <- params$maxp
```

# 1. Model specification and data description

There are data from `r nlevels(as.factor(data[, treat]))` treatments, evaluated using a completely randomized design. The statistical model is
$$
y_{ij} = \mu + \tau_i + \epsilon_{ij}
$$
where

* $y_{ij}$ is the observed response with treatment $i$ and replication $j$.
* $\mu$ is the mean response over all treatments and replications.
* $\tau_i$ is the effect for treatment $i$.
* $\epsilon_{ij}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ij} \sim N(0,\sigma_{\epsilon}^2)$.

```{r, include = FALSE}
out <- NULL
for (i in 1:length(traits))
  out <- c(out, knit_expand('child_crd.Rmd'))
```

`r paste(knit(text = out), collapse = '\n')`
