---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    toc: true
    toc_depth: 3
    highlight: "tango"
params:
  x: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo=FALSE}
x <- params$x
x$IDENTIFIED_CRITERIA <- as.character(x$IDENTIFIED_CRITERIA)
colnames(x) <- c("phase", "Criteria", "Men", "Women", "Global")
x <- tidyr::gather(x, variable, value, Men:Global)

flow <- x[x$phase == "Flowering", ]
harv <- x[x$phase == "Harvest", ]
stor <- x[x$phase == "Storage", ]

temp <- flow[flow$variable == "Global", c("Criteria", "value")]
orden <- temp$Criteria[sort(temp$value, decreasing = T, index.return = T)$ix]
flow$Criteria <- factor(flow$Criteria, levels = orden)

temp <- harv[harv$variable == "Global", c("Criteria", "value")]
orden <- temp$Criteria[sort(temp$value, decreasing = T, index.return = T)$ix]
harv$Criteria <- factor(harv$Criteria, levels = orden)

temp <- stor[stor$variable == "Global", c("Criteria", "value")]
orden <- temp$Criteria[sort(temp$value, decreasing = T, index.return = T)$ix]
stor$Criteria <- factor(stor$Criteria, levels = orden)

nvmflow <- sum(flow[flow$variable == "Men", "value"], na.rm = T)
nvmharv <- sum(harv[harv$variable == "Men", "value"], na.rm = T)
nvmstor <- sum(stor[stor$variable == "Men", "value"], na.rm = T)

nvwflow <- sum(flow[flow$variable == "Women", "value"], na.rm = T)
nvwharv <- sum(harv[harv$variable == "Women", "value"], na.rm = T)
nvwstor <- sum(stor[stor$variable == "Women", "value"], na.rm = T)

nmflow <- round(nvmflow/6)
nmharv <- round(nvmharv/6)
nmstor <- round(nvmstor/6)

nwflow <- round(nvwflow/6)
nwharv <- round(nvwharv/6)
nwstor <- round(nvwstor/6)
```

# 1. Identification of selection criteria and voting process

A group of farmers, men and women, and other stakeholders are gathered and, after explanation of the overall objectives of the trial, they are asked: What do you look for in a new variety of potato when the crop is at the flowering/harvest/post-harvest stage? In other words: When do you say that a variety is good or bad, when evaluating at this stage?

A list is compiled of all the criteria mentioned by the different participants (i.e. free listing). Each criterium is listed and written on a paper bag (or card with accompanying container). Then, in order to select the most important traits for farmers a voting process is conducted.

Farmers are requested to select the three criteria that each considers the most important with the following scheme. They can give:

- Three votes for the most important characteristic.
- Two votes for the second most important characteristic.
- One vote for the third most important characteristic.

Votes are recorded for men and women.

# 2. Flowering

For this face we have the vote of `r nmflow` men and `r nwflow` women.

```{r echo = FALSE}
ggplot2::ggplot(flow, aes(x = variable, y = value, fill = Criteria)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for selection criteria of new varieties at flowering stage", 
       x = "Group", y = "Number of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3.5)
```

# 3. Harvest

For this face we have the vote of `r nmharv` men and `r nwharv` women.

```{r echo = FALSE}
ggplot2::ggplot(harv, aes(x = variable, y = value, fill = Criteria)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for selection criteria of new varieties at harvest stage", 
       x = "Group", y = "Number of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3.5)
```

# 4. Post-harvest (storage)

For this face we have the vote of `r nmstor` men and `r nwstor` women.

```{r echo = FALSE}
ggplot2::ggplot(stor, aes(x = variable, y = value, fill = Criteria)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for selection criteria of new varieties at post-harvest stage", 
       x = "Group", y = "Number of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3.5)
```


