---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    toc: true
    toc_depth: 3
    highlight: "tango"
params:
  x: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo=FALSE}
## Data

x <- params$x
nr <- nlevels(factor(x$REP))
x <- docomp("sum", c("MSM", "MSWM", "MSGLO", "BSM", "BSWM", "BSGLO"), "INSTN", data = x)
x <- tidyr::gather(x, group, value, MSM:BSGLO)
x[x$group %in% c("MSM", "MSWM", "MSGLO"), "trial"] <- "mother"
x[x$group %in% c("BSM", "BSWM", "BSGLO"), "trial"] <- "baby"
x[x$group %in% c("MSM", "BSM"), "group"] <- "Men"
x[x$group %in% c("MSWM", "BSWM"), "group"] <- "Women"
x[x$group %in% c("MSGLO", "BSGLO"), "group"] <- "Global"

## Split by trial

moth <- x[x$trial == "mother", -4]
baby <- x[x$trial == "baby", -4]
both <- docomp("sum", "value", c("INSTN", "group"), data = x)

## Sort by number of votes

temp <- moth[moth$group == "Global", c("INSTN", "value")]
orden <- temp$INSTN[sort(temp$value, decreasing = T, index.return = T)$ix]
moth$INSTN <- factor(moth$INSTN, levels = orden)

temp <- baby[baby$group == "Global", c("INSTN", "value")]
orden <- temp$INSTN[sort(temp$value, decreasing = T, index.return = T)$ix]
baby$INSTN <- factor(baby$INSTN, levels = orden)

temp <- both[both$group == "Global", c("INSTN", "value")]
orden <- temp$INSTN[sort(temp$value, decreasing = T, index.return = T)$ix]
both$INSTN <- factor(both$INSTN, levels = orden)

## Count number of votes

nvmmoth <- sum(moth[moth$group == "Men", "value"], na.rm = T)
nvmbaby <- sum(baby[baby$group == "Men", "value"], na.rm = T)
nvmboth <- nvmmoth + nvmbaby

nvwmoth <- sum(moth[moth$group == "Women", "value"], na.rm = T)
nvwbaby <- sum(baby[baby$group == "Women", "value"], na.rm = T)
nvwboth <- nvwmoth + nvwbaby

## Count number of voters

nmmoth <- round(nvmmoth/6/nr)
nmbaby <- round(nvmbaby/6/nr)

nwmoth <- round(nvwmoth/6/nr)
nwbaby <- round(nvwbaby/6/nr)

## Compute percentage adjusted by gender

mothp <- moth[moth$group == "Global", ]
mothp$value <- mothp$value / (nvmmoth + nvwmoth)
temp <- moth[moth$group != "Global", ]
temp[temp$group == "Men", "value"] <- temp[temp$group == "Men", "value"] / nvmmoth / 2
temp[temp$group == "Women", "value"] <- temp[temp$group == "Women", "value"] / nvwmoth / 2
temp <- docomp("sum", "value", "INSTN", data = temp)
temp$group <- "Global adjusted"
mothp <- rbind(mothp, temp)
mothp$value <- round(mothp$value * 100, 1)

babyp <- baby[baby$group == "Global", ]
babyp$value <- babyp$value / (nvmbaby + nvwbaby)
temp <- baby[baby$group != "Global", ]
temp[temp$group == "Men", "value"] <- temp[temp$group == "Men", "value"] / nvmbaby / 2
temp[temp$group == "Women", "value"] <- temp[temp$group == "Women", "value"] / nvwbaby / 2
temp <- docomp("sum", "value", "INSTN", data = temp)
temp$group <- "Global adjusted"
babyp <- rbind(babyp, temp)
babyp$value <- round(babyp$value * 100, 1)

bothp <- both[both$group == "Global", ]
bothp$value <- bothp$value / (nvmboth + nvwboth)
temp <- both[both$group != "Global", ]
temp[temp$group == "Men", "value"] <- temp[temp$group == "Men", "value"] / nvmboth / 2
temp[temp$group == "Women", "value"] <- temp[temp$group == "Women", "value"] / nvwboth / 2
temp <- docomp("sum", "value", "INSTN", data = temp)
temp$group <- "Global adjusted"
bothp <- rbind(bothp, temp)
bothp$value <- round(bothp$value * 100, 1)
```

# 1. Voting process for the identification of best genotypes at flowering

A group of farmers, men and women, and other stakeholders are gathered and, after explanation of the overall objectives of the trial, they are asked to identify their three personal favorite genotypes. Then, they are requested to vote by giving:

- Three votes for the best genotype.
- Two votes for the second.
- One vote for the third.

Votes are recorded for men and women.

# 2. Best genotypes at the mother plot

There are the votes of `r nmmoth` men and `r nwmoth` women with `r nr` replications (the complete set of genotypes has been planted `r nr` times, and each men and women have voted for each replication).

```{r echo = FALSE, fig.height = 5, fig.width = 8}
ggplot(moth, aes(x = group, y = value, fill = INSTN)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for best genotypes at flowering stage", 
       x = "Group", y = "Number of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3)
```

Below a percentage graph is shown. On the right panel the percentages are adjusted by gender, thus trying to reflect what would have been obtained if the number of men and women would be the same in the sample.

```{r echo = FALSE, fig.height = 5, fig.width = 8}
ggplot(mothp, aes(x = group, y = value, fill = INSTN)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for best genotypes at flowering stage in the mother plot",
       subtitle = "Percentages unadjusted and adjusted by gender",
       x = "Group", y = "Percentage of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3)
```

# 3. Best genotypes at the baby plots

There are the votes of `r nmbaby` men and `r nwbaby` women with `r nr` replications (the complete set of genotypes has been planted `r nr` times, and each men and women have voted for each replication).

```{r echo = FALSE, fig.height = 5, fig.width = 8}
ggplot(baby, aes(x = group, y = value, fill = INSTN)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for best genotypes at flowering stage in the baby plots", 
       x = "Group", y = "Number of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3)
```

Below a percentage graph is shown. On the right panel the percentages are adjusted by gender, thus trying to reflect what would have been obtained if the number of men and women would be the same in the sample.

```{r echo = FALSE, fig.height = 5, fig.width = 8}
ggplot(babyp, aes(x = group, y = value, fill = INSTN)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for best genotypes at flowering stage in the baby plots",
       subtitle = "Percentages unadjusted and adjusted by gender",
       x = "Group", y = "Percentage of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3)
```

# 4. Best genotypes at both, mother and baby plots

There are the votes of `r nmmoth` men and `r nwmoth` women in the mother plot and `r nmbaby` men and `r nwbaby` women at the baby plots with `r nr` replications in each case.

```{r echo = FALSE, fig.height = 5, fig.width = 8}
ggplot(both, aes(x = group, y = value, fill = INSTN)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for best genotypes at flowering stage in the mother and baby plots", 
       x = "Group", y = "Number of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3)
```

Below a percentage graph is shown. On the right panel the percentages are adjusted by gender, thus trying to reflect what would have been obtained if the number of men and women would be the same in the sample.

```{r echo = FALSE, fig.height = 5, fig.width = 8}
ggplot(bothp, aes(x = group, y = value, fill = INSTN)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") + 
  labs(title = "Voting for best genotypes at flowering stage in the mother and baby plots",
       subtitle = "Percentages unadjusted and adjusted by gender",
       x = "Group", y = "Percentage of votes") +
  geom_text(aes(label = value), vjust = 1.6, color = "white",
             position = position_dodge(0.9), size = 3)
```
