---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    toc: true
    toc_depth: 3
    highlight: "tango"
params:
  data: "no data"
  form: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo=FALSE}

## Data

data <- params$data
colnames(data)[2:4] <- c("Appe", "Tast", "Text")

## Count number of men and women

temp <- data[data$Sex == "M" | data$Sex == "Male", ]
nm <- nlevels(factor(temp$PanelNo))
temp <- data[data$Sex == "F" | data$Sex == "Female", ]
nw <- nlevels(factor(temp$PanelNo))

## Format data

datag <- docomp("sum", c("Appe", "Tast", "Text"), "INSTN", data = data)
data <- docomp("sum", c("Appe", "Tast", "Text"), c("INSTN", "Sex"), data = data)
datam <- data[data$Sex == "M" | data$Sex == "Male", ]
dataf <- data[data$Sex == "F" | data$Sex == "Female", ]
colnames(datam)[3:5] <- c("Appe-M", "Tast-M", "Text-M")
colnames(dataf)[3:5] <- c("Appe-F", "Tast-F", "Text-F")
data <- cbind(datam[, c(1, 3:5)], dataf[, 3:5])

rownames(data) <- data$INST
rownames(datag) <- datag$INSTN

data <- data[, -1]
datag <- datag[, -1]

```

# 1. Gathering of data

Samples of all genotypes are boiled and presented on plates. Each genotype is evaluated about appearance and taste with the options:

- 5 excellent,
- 3 fair,
- 1 poor,

and about texture with:

- 5 mealy or floury,
- 3 intermediate,
- 1 soggy or watery.

For the graphs below, the following abbreviations are used:

- `Appe`: Appearance.
- `Tast`: Taste.
- `Text`: Texture.
- `Appe-M`: Men opinion on appearance.
- `Tast-M`: Men opinion on taste.
- `Text-M`: Men opinion on texture.
- `Appe-W`: Women opinion on appearance.
- `Tast-W`: Women opinion on taste.
- `Text-W`: Women opinion on texture.

# 2. Results

A principal components analysis is shown to see the associations among the genotypes and the attributes, first with all the panelists together and then with panelists opinions differentiated by gender.

```{r echo = FALSE, fig.height = 6, fig.width = 6}
princip <- prcomp(datag, center = T, scale. = T)
summary(princip)
factoextra::fviz_pca(princip, repel = T,
                     title = "Biplot of genotypes and attributes")
```

```{r echo = FALSE, fig.height = 6, fig.width = 6}
princip <- prcomp(data, center = T, scale. = T)
summary(princip)
factoextra::fviz_pca(princip, repel = T,
                     title = "Biplot of genotypes and attributes by gender")
```
