---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    toc: true
    toc_depth: 3
    highlight: "tango"
params:
  x: "no data"
  form: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo=FALSE}

## Data

x <- params$x
colnames(x)[2:4] <- c("Appearance", "Taste", "Texture")

## Count number of men and women

temp <- x[x$Sex == "M", ]
nm <- nlevels(factor(temp$PanelNo))
temp <- x[x$Sex == "F", ]
nw <- nlevels(factor(temp$PanelNo))

## Format data

xg <- docomp("sum", c("Appearance", "Taste", "Texture"), "INSTN", data = x)
x <- docomp("sum", c("Appearance", "Taste", "Texture"), c("INSTN", "Sex"), data = x)
xm <- x[x$Sex == "M", ]
xf <- x[x$Sex == "F", ]
colnames(xm)[3:5] <- c("Appearance-M", "Taste-M", "Texture-M")
colnames(xf)[3:5] <- c("Appearance-F", "Taste-F", "Texture-F")
x <- cbind(xm[, c(1, 3:5)], xf[, 3:5])

rownames(x) <- x$INST
rownames(xg) <- xg$INSTN

x <- x[, -1]
xg <- xg[, -1]

```

# 1. Gathering of data

Samples of all genotypes are boiled and presented on plates. Each genotype is evaluated by `r nm` men and `r nw` women about appearance and taste with the options:

- 5 excellent,
- 3 fair,
- 1 poor,

and about texture with:

- 5 mealy or floury,
- 3 intermediate (3),
- 1 soggy or watery.

# 2. Results

A principal components analysis is shown to see the associations among the genotypes and the attributes, first with all the panelists together and then with panelists opinions differentiated by gender.

```{r echo = FALSE, fig.height = 6, fig.width = 6}
princip <- prcomp(xg, center = T, scale. = T)
summary(princip)
factoextra::fviz_pca(princip, repel = T,
                     title = "Biplot of genotypes and attributes")
```

```{r echo = FALSE, fig.height = 6, fig.width = 6}
princip <- prcomp(x, center = T, scale. = T)
summary(princip)
factoextra::fviz_pca(princip, repel = T,
                     title = "Biplot of genotypes and attributes by gender")
```
