---
title: "Report for a MET with a RCBD"
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
  pdf_document:
    toc: true
    highlight: zenburn
  word_document:
    highlight: "tango"
params:
  trait: "no data"
  geno: "no data"
  env: "no data"
  rep: "no data"
  data: "no data"
  maxp: "no data"
  author: "no data"
---

```{r, echo = FALSE}
trait <- params$trait
geno <- params$geno
env <- params$env
rep <- params$rep
data <- params$data
maxp <- params$maxp

orig <- data
lc <- st4gi::checkdata02(trait, geno, env, rep, data)
at <- suppressWarnings(st4gi::aovmet(trait, geno, env, rep, data, maxp))
if (lc$c3 == 0)
  data[, trait] <- st4gi::mvemet(trait, geno, env, rep, data, maxp)[, 5]
model <- aov(data[, trait] ~ data[, geno] + data[, env]
             + data[, rep] %in% data[, env] + data[, geno]:data[, env])
```

# 1. Model specification and data description

There is data from `r nlevels(as.factor(data[, env]))` environments and `r nlevels(as.factor(data[, geno]))` genotypes. In each environment the genotypes were evaluated using a randomize complete block design with `r nlevels(as.factor(data[, rep]))` blocks. The statistical model is
$$
y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \gamma_{k(j)} + \epsilon_{ijk}
$$
where

* $y_{ijk}$ is the observed response with genotype $i$, environment $j$, and block $k$ nested in environment $j$.
* $\mu$ is the mean response over all genotypes, environments and blocks.
* $\alpha_i$ is the fixed effect for genotype $i$.
* $\beta_j$ is the fixed effect for environment $j$.
* $(\alpha\beta)_{ij}$ is the fixed interaction effect between genotype $i$ and environment $j$.
* $\gamma_{k(j)}$ is the random effect of block $k$ nested in environment $j$.
* $\epsilon_{ijk}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ijk} \sim N(0,\sigma_{\epsilon}^2)$.

# 2. Analysis of `r trait`

`r if(lc$c3 == 1) {"There are no missing values for this trait; the design es balanced."}`

`r if(lc$c3 == 0) paste("There are some missing values (", format(lc$pmis * 100, digits = 3), "%) and they have been estimated for the descriptive statistics and ANOVA sections.")`

## 2.1. Descriptive statistics

#### Means by genotypes

```{r, echo = FALSE}
tapply(data[, trait], data[, geno], mean)
```

#### Means by environments

```{r, echo = FALSE}
tapply(data[, trait], data[, env], mean)
```

#### Means by genotypes and environments

```{r, echo = FALSE}
tapply(data[, trait], list(data[, geno], data[, env]), mean)
```

## 2.2. ANOVA

### 2.2.1. Checking assumptions

As it was stated in section 1, it is supposed that the error has a normal distribution with the same variance for all the genotypes and evironments. The following plots help to evaluate this assumptions:

```{r, echo = FALSE, fig.height = 5, fig.width = 10}
par(mfrow = c(1, 2))
plot(model, which = 1)
plot(model, which = 2)
```

Funnel shapes for the first plot may suggest heterogeneity of variances while departures from the theoretical normal line are symptoms of lack of normality.

### 2.2.2. ANOVA table

```{r, echo = FALSE}
at
```
The p-values for the model are:

- `r format(at[1, 5], digits = 4)` for genotypes `r if(at[1, 5] < 0.05) {"which is significant at the 5% level."} else {"which is not significant at the 5% level."}`
- `r format(at[2, 5], digits = 4)` for environments `r if(at[2, 5] < 0.05) {"which is significant at the 5% level."} else {"which is not significant at the 5% level."}`
- `r format(at[4, 5], digits = 4)` for the genotypes by environments interaction `r if(at[4, 5] < 0.05) {"which is significant at the 5% level."} else {"which is not significant at the 5% level."}`

## 2.3. Stability analysis

`r if(at[4, 5] > 0.05) {"Because interaction is non significant a stability analysis is not presented."}`
`r if(at[4, 5] < 0.05) {"Because interaction is significant a stability analysis is presented."}`

`r if(at[4, 5] < 0.05) {"### 2.3.1. AMMI"}`

`r if(at[4, 5] < 0.05) {"#### AMMI biplots"}`
```{r, echo = FALSE, fig.height = 7, fig.width = 7}
if(at[4, 5] < 0.05) {
  ammimodel <- ammi(trait, geno, env, rep, orig, biplot = 1)
  ammimodel <- ammi(trait, geno, env, rep, orig, biplot = 2)
}
```

`r if(at[4, 5] < 0.05) {"#### Interaction effects"}`
```{r, echo = FALSE}
if(at[4, 5] < 0.05) ammimodel$Interaction_effects
```

`r if(at[4, 5] < 0.05) {"#### PC-values for genotypes"}`
```{r, echo = FALSE}
if(at[4, 5] < 0.05) ammimodel$PC_values_genotypes
```

`r if(at[4, 5] < 0.05) {"#### PC-values for environments"}`
```{r, echo = FALSE}
if(at[4, 5] < 0.05) ammimodel$PC_values_environments
```

`r if(at[4, 5] < 0.05) {"#### PC contributions"}`
```{r, echo = FALSE}
if(at[4, 5] < 0.05) ammimodel$Contribution_PCs
```

`r if(at[4, 5] < 0.05) {"### 2.41. Tai stability analysis"}`

`r if(at[4, 5] < 0.05) {"#### Tai plot"}`
```{r, echo = FALSE, fig.height = 7, fig.width = 7}
if(at[4, 5] < 0.05)
  taimodel <- tai(trait, geno, env, rep, orig)
```

`r if(at[4, 5] < 0.05) {"#### Tai alpha and lambda values"}`
```{r, echo = FALSE}
if(at[4, 5] < 0.05)
  taimodel
```
