---
title: "Descriptive report for a numeric trait"
author: "International Potato Center"
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
  pdf_document:
    toc: true
    highlight: zenburn
  word_document:
    highlight: "tango"
params: 
  x: "no data"
---

```{r, echo = FALSE}
nt = params$x
```

It looks like you have a numeric trait on a quantitative scale. A descriptive summary tells you that
```{r, echo = FALSE}
output <- summary(nt)
output
```
the minimum is `r output[[1]]`, the maximum `r output[[6]]`, the median `r output[[3]]`, and the mean `r output[[4]]`. A boxplot could be a suitable plot for these data:

```{r, echo = FALSE}
boxplot(nt)
```

```{r, echo = F}
# Compute skewness parameter
sk <- 3*(mean(nt) - median(nt))/sd(nt)
```

`r if(sk > 0.5) {"It looks like you have some positive skewness because your mean is quite larger than your median. Watch out with this if you want to fit a model that assumes normality." }`

`r if(sk < -0.5) {"It looks like you have some negative skewness because your mean is quite smaller than your median. Watch out with this if you want to fit a model that assumes normality." }`
