---
title: "Pesek Baker index"
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
  pdf_document:
    toc: true
    highlight: zenburn
  word_document:
    highlight: "tango"
params: 
  traits: "no data"
  geno: "no data"
  env: "no data"
  rep: "no data"
  data: "no data"
  means: "no data"
  model: "no data"
  dgg: "no data"
  units: "no data"
  sf: "no data"
  author: "no data"
---

```{r, echo = FALSE}
traits <- params$traits
geno <- params$geno
env <- params$env
rep <- params$rep
data <- params$data
means <- params$means
model <- params$model
dgg <- params$dgg
units <- params$units
sf <- params$sf

pbindex <- pesekbaker(traits, geno, env, rep, data, means, model, dgg, units, sf)
```

### Desired genetic gains
You have computed the Pesek-Baker index for traits `r traits` with the following desired genetic gains in actual units:
```{r, echo = FALSE}
pbindex$Desired.Genetic.Gains
```

### Standard deviations, genetic variances, and correlations
The estimated standard deviations for these traits are
```{r, echo = FALSE}
pbindex$Standard.Deviations
```
the genetic variances
```{r, echo = FALSE}
pbindex$Genetic.Variances
```
and the correlation matrix among the traits included in the index computation
```{r, echo = FALSE}
pbindex$Correlation.Matrix
```

### The Pesek-Baker index

The index coefficients for the Pesek-Baker index are:
```{r, echo = FALSE}
pbindex$Index.Coefficients
```

With this, the Pesek-Baker index for each genotype is shown below. As you see, genotype `r (pbindex$Pesek.Baker.Index[sort(pbindex$Pesek.Baker.Index$PB.Index, decreasing = T, index.return = T)$ix, ])[1,1]` is the one with the highest value.
```{r, echo = FALSE}
pbindex$Pesek.Baker.Index[sort(pbindex$Pesek.Baker.Index$PB.Index, decreasing = T,
                               index.return = T)$ix, ]
```

`r if(model == 'gxe') {"### The response to selection"}`

`r if(model == 'gxe') paste("For a selection fraction of ", sf, ", the response to selection in actual units for traits", sep = "")`
`r if(model == 'gxe') traits`
`r if(model == 'gxe') {"is"}`

```{r, echo = FALSE}
if(model == 'gxe') pbindex$Response.to.Selection
```

`r if(model == 'gxe') {"and in standardized units"}`

```{r, echo = FALSE}
if(model == 'gxe') pbindex$Std.Response.to.Selection
```
